MSCA 31006: Final Project - AQI Forecasting

### 2023-08-16 MSCA_31006_Time_Series_Final_Project - TBATS.Rmd
Add files via upload

mae <- mean(abs(test_weekly - forecast_tbats$mean))
print(cat("Mean Absolute Error (MAE):", round(mae, 2), "\n"))
#Mean Absolute Error (MAE): 9.31 
mape <- mean(abs(test - forecast_tbats$mean)/test * 100)
cat("Mean Absolute Percentage Error (MAPE):", round(mape, 2), "\n")

@@

model_tbats$lambda
model_tbats$alpha
model_tbats$beta
model_tbats$seasonal.periods
model_tbats$p
model_tbats$q
model_tbats$likelihood
model_tbats$AIC

>>>>

mae <- mean(abs(test_weekly - forecast_tbats$mean))
print(cat("Mean Absolute Error (MAE):", round(mae, 2), "\n"))
#Mean Absolute Error (MAE): 9.31 
smape_tbats_weekly <- smape(test_weekly, forecast_tbats$mean)
print(cat("Symmetric Mean Absolute Percentage Error (MAPE):", round(smape_tbats_weekly, 4), "\n"))
rmse <- rmse(test_weekly, forecast_tbats$mean)
print(cat("Root Mean Squared Error (RMSE):", round(rmse, 2), "\n"))

@@

model_tbats$lambda
model_tbats$alpha
model_tbats$beta
model_tbats$seasonal.periods
model_tbats$ar.coefficients
model_tbats$ma.coefficients
model_tbats$p
model_tbats$q
model_tbats$likelihood
model_tbats$AIC
